%-------------------------
% Resume in Latex
% Original Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{xcolor}
\definecolor{linkcolor}{HTML}{0645AD} % a softer web-link blue
\usepackage[pdftex,colorlinks=true,urlcolor=linkcolor]{hyperref}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\renewcommand{\labelitemiii}{$\bullet$}

\newcommand{\resumeItemNoTitle}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\small#1} & #2 \\
      \textit{#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Mike Freyberger}} & Mobile : +1-908-421-3715 \\
  \href{http://www.linkedin.com/in/michael-freyberger-933a5b53}{www.linkedin.com/in/michael-freyberger-933a5b53} & Email : \href{mailto:mike.freyberger@gmail.com}{mike.freyberger@gmail.com}\\
\end{tabular*}

%-----------WORK EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Scope3 (Advertising Sustainability Platform)}{Jan 2022 -- Present}
      {Co-Founder \& CTO}{New York, NY / Remote}
      \resumeItemListStart
        \resumeItemNoTitle{\textbf{Co-founded advertising sustainability platform} as one of 3 founding engineers, architecting first-ever carbon emissions model for digital advertising using graph-based supply chain analysis.}
        \resumeItemNoTitle{Built foundational data pipeline and high-throughput API platform using \textbf{Airflow, BigQuery, Dataflow, Pub/Sub, and Google Kubernetes Engine}, enabling transition from manual file delivery to programmatic access for enterprise clients and major ad tech companies.}
        \resumeItemNoTitle{Led technical strategy enabling \textbf{\$45M raised across two Series B rounds} from Google Ventures by demonstrating platform scalability and infrastructure reliability to board of directors as CTO.}
        \resumeItemNoTitle{Scaled engineering organization from 3 founding engineers to \textbf{35-person team} across multiple products, developing senior engineers into lead roles, hiring engineering managers, and mentoring director of engineering who became head of engineering.}
        \resumeItemNoTitle{Architected real-time infrastructure supporting \textbf{1M+ QPS} with $<$10ms latency requirements, negotiating \textbf{90\% cost reduction} in network egress and enabling global bare metal deployment.}
        \resumeItemNoTitle{Pioneered \textbf{industry-first placement-level optimization} using viewability data, leading technical solutioning and development with ShareThrough and Index Exchange as launch partners.}
        \resumeItemNoTitle{Built self-service measurement platform with Temporal for event-based orchestration and ClickHouse for sub-second reporting.}
        \resumeItemNoTitle{Measured over \textbf{1 trillion ad impressions} across 100+ enterprise clients, featuring native integrations with Google, Trade Desk, Amazon, and Meta.}
        \resumeItemNoTitle{Launched agentic advertising platform using custom LLM-powered brand safety system with real-time infrastructure enabling content-to-classification and live campaign activation within \textbf{10 seconds}.}
      \resumeItemListEnd
    \resumeSubheading
      {Waybridge (Commodities Trading Platform)}{Oct 2019 -- Dec 2021}
      {Founding Engineer/Engineering Manager}{New York, NY / Remote}
      \resumeItemListStart
        \resumeItemNoTitle{Founding engineer on 3-person team that built Waybridge's commodities trading platform from ground up, determining product-market fit through rapid iteration with early clients.}
        \resumeItemNoTitle{Led critical technical migrations including REST to GraphQL conversion and built trade amendment system enabling real-time modifications to booked trades.}
        \resumeItemNoTitle{\textbf{Managed critical SAP integration with largest client} through daily stakeholder engagement and 24/7 system monitoring, ensuring seamless production rollout while building reusable ERP adapter framework.}
        \resumeItemNoTitle{Scaled from IC to engineering manager leading 4-engineer team while maintaining technical contributions, improving API performance by \textbf{20x} on critical GraphQL queries.}
      \resumeItemListEnd
    \resumeSubheading
      {AppNexus (Advertising Technology, acquired by AT\&T)}{Sept 2016 -- Oct 2019}
      {Senior Software Engineer, Team Lead}{New York, NY}
      \resumeItemListStart
        \resumeItemNoTitle{Took ownership within months of the core pricing components in AppNexus's low-latency, distributed ad-serving platform (serving \textbf{billions of daily transactions}).}
        \resumeItemNoTitle{Rapidly promoted to tech lead for a \textbf{7-engineer cross-functional team} building exchange-traded media products.}
        \resumeItemNoTitle{Led company-wide transparency initiatives as both tech lead and product manager; acted as primary technical contact for Amino Payments and other blockchain partners. Delivered multiple external talks, including \textit{Is Blockchain Ready for AdTech?} \href{https://www.youtube.com/watch?v=mGBcOz2Sp9Q}{[Talk]}.}
        \resumeItemNoTitle{Designed and launched Transaction Resolver, a full replacement for AppNexus's streaming pipeline determining which ad auctions transacted (\textbf{1.5M+ messages}, \textbf{200K+ transactions}, \textbf{0.5GB/sec throughput}). Presented the architectural design at DeveloperWeek NYC 2018 \href{https://docs.google.com/presentation/d/1v_3tCqZP_-gqlv7hp-89Y0mVkBWHtjPJuplmwbf43ds/edit?usp=sharing}{[Slides]}.}
        \resumeItemNoTitle{Transitioned into engineering management, leading a forecasting team and driving architectural cost reductions by deprecating legacy systems.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Princeton University}{Sept 2012 -- May 2016}
      {B.S.E., Electrical Engineering, Magna Cum Laude}{Princeton, NJ}
      \resumeItemListStart
        \resumeItemNoTitle{GPA 3.88; inducted into Phi Beta Kappa, Tau Beta Pi, and Sigma Xi honor societies.}
        \resumeItemNoTitle{Awarded the \textbf{Charles Ira Young Memorial Medal} for top research in Electrical Engineering.}
        \resumeItemNoTitle{Senior thesis published at PETS 2018: \textit{Cracking ShadowCrypt} \href{https://petsymposium.org/2018/files/papers/issue2/popets-2018-0012.pdf}{[Paper]}, \href{https://youtu.be/7p0IGo14XcU}{[Talk]}.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}